Brief notes on erosion

### 2020-08-07 docs/proposals/NSF/budgets/budgetJustUSNA.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of the
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added: \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
    \hline
    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
    \hline
    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10849.85
$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added: \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
    \hline
    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
    \hline
    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10,849.85
$ \\
    \hline
  \end{tabular}
\end{center}
